Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-12 paper.tex
Update paper.tex

The process of domestication was once thought to be rapid and geographically constrained, with crops originating from a wild progenitor within one or more geographically defined centers followed by expansion to the modern-day extent of cultivation. \mbh{will need citation for this}
However, archaeological and genetic evidence are beginning to reveal that, in many cases, domestication has been temporally protracted and more diffuse \cite{brown2009complex}. \mbh{citations here to Li's paper, Purugganan rice paper, Brandon Gaut's recent grape paper}
This new conception of domestication emphasizes the role of beneficial gene flow (\emph{i.e.}, adaptive introgression) from locally adapted wild relatives during crop expansion after initial domestication.

>>>>

The process of domestication was once thought to be rapid and geographically constrained, with crops originating from a wild progenitor within one or more geographically defined centers followed by expansion to the modern-day extent of cultivation. \mbh{will need citation for this}
\gmj{ the paper "Domestication rates in wild-type wheats and
barley under primitive cultivation" states that domestication could have taken place in as little as 20 or 30 years.}
However, archaeological and genetic evidence are beginning to reveal that, in many cases, domestication has been temporally protracted and more diffuse \cite{brown2009complex}. \mbh{citations here to Li's paper, Purugganan rice paper, Brandon Gaut's recent grape paper} \gmj{also include the paper I just read, "ARCHAEOLOGICAL DATA REVEAL SLOWRATES OF EVOLUTION DURING PLANTDOMESTICATION".  This paper suggests that the rate of phenotypic change in domestication is slower than expected, nearly that of natural selection in wild populations.  Also, see the first paragraph of the Discussion for a list of older papers supporting rapid domestication.}
This new conception of domestication emphasizes the role of beneficial gene flow (\emph{i.e.}, adaptive introgression) from locally adapted wild relatives during crop expansion after initial domestication.
